Photovoltaic System Reconfiguration strategy for mismatch condition\\ {\footnotesize \textsuperscript{}}

### 2018-08-14 main.tex
20180814

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

@@

\begin{itemize}
\item The current versus voltage (\textit{I-V}) curve of each panel calculated by algorithm presented in \cite{b6}. This algorithm will analyzes panel's \textit{I-V} curve sample and coordinate to maximum or minimum power point in \textit{P-V} curve.
\item All the panels in PV array have same number (\textit{N}) of modules. For particular module, using (\textit{$V_{mppn}$, $I_{mppn}$}) to identify MPP voltage and current by index \textit{n}. Those parameter can be directly estimated by the prosess provided in\cite{b7}.
\end{itemize}

@@

When there are more than two panels connected in series, for a string MPPs is not straightforward. The MPP current and voltage candidates can be evaluated though a procedure presented in \cite{b10}.

>>>>

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

@@

\begin{itemize}
\item The current versus voltage (\textit{I-V}) curve of each panel calculated by algorithm presented in \cite{b6}. This algorithm will analyzes panel's \textit{I-V} curve sample and coordinate to maximum or minimum power point in \textit{P-V} curve.
\item All the panels in PV array have same number (\textit{N}) of modules. For particular module, using (\textit{$V_{mpp_n}$, $I_{mpp_n}$}) to identify MPP voltage and current by index \textit{n}. Those parameter can be directly estimated by the prosess provided in\cite{b7}.
\end{itemize}

@@

When there are more than two panels connected in series, for a string MPPs is not straightforward. The MPP current and voltage candidates can be evaluated though a procedure presented in \cite{b10}. For string MPP current candidates, \textit{$I_{mpp_n}$} values' different less than 5\% are assumed to be equal. For string MPP voltage candidates, \textit{$V_{mpp_n}$}  can be calculated though multiplay number of active modules \textit{$M_a$} by average MPP voltages \textit{$\bar V_{mpp}$} with $\pm$18\% error \cite{b10}.
